\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-09-25 papers/methods/paper.tex
Updating paper for Dan

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{tikz}
\usepackage{enumerate}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\usetikzlibrary{bayesnet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}
	\centering
	\caption{ Parameters defined in our model and a summary of their use. The parameters are broken into multiple sections, the top for parameters which are defined globally across all surveys, the second section for parameters which are defined for each survey, the third section are parameters which are defined for each supernova. The bottom section shows the observables (not parameters) that are the input data to the model.}
	\label{tab:param_summary}
	\begin{tabular}{ll}
		\hline
		Parameter & Description \\
		\hline
		$\Omega_m$  & Matter density  \\
		$w$  &  Dark energy equation of state  \\
		$\alpha$ & Stretch standardisation   \\
		$\beta$         &  Colour standardisation   \\
		$\delta(0)$ & Scale of the mass-magnitude correction\\
		$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
		$\delta\mathcal{Z}_i$ & Systematics scale\\
		$\delta S$ & Selection effect deviation \\
		$\langle M_B \rangle$ & Mean absolute magnitude \\
		%$s_c$ & Colour bias\\
		\hline
		$\langle x_1^i \rangle$ & Mean stretch nodes\\
		$\langle c^i \rangle$ & Mean colour nodes\\
		$\alpha_c$ & Skewness of colour population \\
		$\sigma_{M_B}$ & Population magnitude scatter \\
		$\sigma_{x_1}$ & Population stretch scatter \\
		$\sigma_{c}$ & Population colour scatter \\
		$\kappa_{0}$ & Extra colour dispersion\\
		$\kappa_{1}$ & Redshift-dependence of extra colour dispersion\\
		\hline
		$m_B$ & True flux\\
		$x_1$ & True stretch \\
		$c$ & True colour \\
		$z$ & True redshift \\
		$M_B$ & Derived absolute magnitude \\
		$\mu$ & Derived distance modulus \\
		\hline
		$\hat{m}_B$ & Measured flux\\
		$\hat{x}_1$ & Measured stretch \\
		$\hat{c}$ & Measured colour \\
		$C$ & Covariance on flux, stretch and colour \\
		$\hat{z}$ & Observed redshift \\
		$\hat{m}$ & Determined mass probability \\
		$\hat{p}$ & Determined outlier probability \\
		\hline
	\end{tabular}
\end{table}

@@

	\node[det, above=of z] (mu) {$\mu$};
	\node[latent, right=4.33cm of mu] (MBobs) {$M_B$};
	% Survey nodes
	\node[latent, above=of sum, yshift=1cm,text width=2.7cm, align=center] (pop1) {$\langle x_1^i \rangle, \langle c^i \rangle,\rho,\sigma_{M_B}, $\\$ \sigma_{x_1}, \sigma_c, \alpha_c, \kappa_0, \kappa_1$ };
	\node[latent, right=1.5cm of pop1, align=center] (sf) {$\Delta_i, \delta_i$};
	% Global nodes
	\node[latent, above=2cm of mu]  (cosmo) {$\Omega_m, w$};
	\node[latent, above=1.7cm of MBobs, text width=3cm, align=center]  (ab) {$\langle M_B \rangle, \alpha, \beta$, $\delta(0)$, \\$\delta(\infty)$, $\delta \mathcal{Z}_i$, $\delta S$};

@@

In addition to the improvements in the scatter models over the simple data, we also include peculiar velocities for the LowZ sample, and our full treatment of systematics. Our simulated populations are sourced from \citet[][hereafter {\sk}]{Scolnic2016} and shown in Table \ref{tab:dist}. Initial tests were also done with a second, Gaussian population with colour and stretch populations centered on zero and with respective width $0.1$ and $1$, however cosmological parameters were not impacted by choice of the underlying population and we continue using only the {\sk} population for computational efficiency. The selection effects were quantified by comparing all the generated supernovae to those that pass our simulated cuts, as shown in Figure~\ref{fig:sf_snana}. It is from this simulation that our analytic determination of the selection functions for the LowZ and DES survey are based. {\green We run two simulations to determine the efficiency using the {\gten} and {\celeven} scatter models and find no difference in the selection effect of Malmquist bias between the two models.}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_points_g10.pdf}		\includegraphics[width=\columnwidth]{bulk_points_c11.pdf}
	\end{center}
	\caption{Maximum posterior points for 100 realisations of supernova data for two intrinsic dispersion models - the {\gten} model for the top panel and the {\celeven} model for the bottom panel. Points are shown for parameters $\Omega_m$, $w$, $\alpha$, $\beta$ and $\langle M_B \rangle$, with the other fit parameters being marginalised over. As we are unable to fully correct observed summary statistics, a step required by the lack of intrinsic scatter in the SALT2 model, we expect to see an offset in $\alpha$ and $\beta$. This in turn effects cosmology, resulting in small biases in $w$.}
	\label{fig:bulk_posterior}
\end{figure}

\begin{table}
	\centering
	\caption{Investigating the combined 100 fits to {\gten} and {\celeven} simulations, fitting with both statistics only and also when including systematics. The quoted value for $w$ represents the average mean of the fits, with the uncertainty being the average standard deviation of the fits. In brackets, the simulation scatter (the standard deviation of the mean of 100 fits) is shown, and the bias significance represents our confidence that the deviation in the mean $w$ away from $-1$ is not due to statistical fluctuation. With systematics enabled, both the {\gten} and {\celeven} models show evidence of bias, scattering to either side of the simulated value of $w=-1$. However, their deviation from the truth value represents a shift of approximately $0.5\sigma$ when taking into account the uncertainty on fits to $w$. The bias is sub-dominant to both the size of the uncertainty for each fit, and the scatter induced by statistical variance in the simulations. We also note that the simulations do not vary cosmological parameters nor population. As our model does include uncertainty on those values, the simulation scatter is expected to be less than the model uncertainty, and represents a minimum bound on permissible uncertainty values.}
	\label{tab:bulk_summary}
	\begin{tabular}{l|cc}
		\hline
		Model & $w$ (scatter) & Bias \\
		\hline
		{\gten} Stat + Syst  &  $-1.00\pm 0.10\ (0.08)$ & $0.0\sigma$  \\
		{\celeven} Stat + Syst  &  $-0.95\pm 0.10\ (0.06)$ & $0.5\sigma$  \\
		{\gten}  Stat         &  $-1.00\pm 0.08\ (0.08)$ & $0.0\sigma$   \\
		{\celeven} Stat         &  $-0.95\pm 0.08\ (0.05)$ & $0.6\sigma$   \\
		\hline
	\end{tabular}
\end{table}

@@

Points of maximum posterior for 100 data realisations are shown in Figure \ref{fig:bulk_posterior}. The parameter bounds are listed in Table \ref{tab:bulk_summary}. {\green Our recovered results are all within $0.5\sigma$ of the true values of $\Omega_m = 0.3$, $w=-1$.}

@@

Unfortunately, adding extra fit parameters to allow for shifting observables washes out our ability to constrain cosmology, and applying a specific bias correction requires running a fiducial simulation (assuming cosmology, population and scatter model) and binning data. It is difficult to do whilst accounting for correlations with population and scatter model. This is compounded by the fact that bias corrections do not in general improve fits (increase the log posterior), and so are difficult to fit inherently. Works such as \citet{Kessler2017} show that bias corrections can be applied to supernovae datasets that can robustly handle multiple intrinsic scatter models, and future work will center on uniting these methodologies - incorporating better bias corrections that separate intrinsic scatter bias and non-Gaussian summary statistic bias from Malmquist bias, without having to precompute standardisation parameters and populations.

@@

Table \ref{tab:parameter_correlations} lists the fit correlations between our model fit parameters (excluding the LowZ band systematics, and Malmquist bias uncertainty parameters which had negligible correlation), showing (in order) cosmological parameters, standardisation parameters, population width and skewness parameters, intrinsic dispersion parameters, mass-step parameters, population mean parameters, SALT2 model systematics, dust systematic, global HST calibration systematic, peculiar velocity systematic, global redshift systematic and DES band magnitude and wavelength systematics. Figure \ref{fig:bulk_cor} show the full correlations between all non-systematic model parameters. As expected, $w$ bias would be introduced primarily through incorrectly determined standardisation parameters and mean absolute magnitude, which itself is tied to the unexplained colour dispersion and biases in colour introduced by the unknown intrinsic scatter model. Other interesting correlations are shown and discussed in Figure \ref{fig:bulk_cor}. The band systematics for DES filters $g$, $r$ and $i$ also show significant correlation with $w$, highlighting the importance of minimising instrumental uncertainty.

@@

@@

\begin{table}
	\centering
	\caption{The error budget on $w$, as determined from analysing uncertainty on simulation data whilst progressively enabling model features. We start from the top of the table, only varying cosmological parameters $\Omega_m$ and $w$, and then progressively unlock parameters and let them fit as we progress down the table. The cumulative uncertainty shows the total uncertainty on $w$ on the fit for all, where the $\sigma_w$ term is derived by taking the quadrature difference in cumulative uncertainty as we progress.}
	\label{tab:uncert}
	\begin{tabular}{l|rr}
		Feature & $\sigma_w$ & Cumulative  \\
		\hline
		Cosmology only                 & 0.051  &   0.051       \\
		Standardisation parameters     & 0.046  &   0.068       \\
		Intrinsic scatter              & 0.020  &   0.071       \\
		Redshift-independent populations      & 0.022  &   0.074       \\
		Redshift-dependent populations & 0.030  &   0.080       \\
		Systematics                    & 0.054  &   0.096       \\
		\hline
	\end{tabular}
\end{table}

@@

{\green As shown in GET-BROUT-CITATION, BBC recovers cosmological parameters without bias so long as the intrinsic scatter model is known. As we do not know the correct intrinsic scatter model, the BBC method averages the results when using bias corrections from {\gten} and from {\celeven}. As such, we expect the BBC method to be biased in one direction for {\gten} simulations and the other direction for {\celeven} simulations. These results are consistent with those displayed in Table \ref{tab:bulk_summary_bbc}, as both} BBC and BHM are sensitive to the intrinsic scatter model, finding differences of $\sim0.06$ in $w$ when varying the scatter model. The BBC method finds $w$ biased low for G10 and $w$ biased high for C11 (by about $\pm0.03$), so taking the average result only results in a small bias of $-0.01$ in $w$. Our method shows a small improvement in the insensitivity to the intrinsic scatter model, finding no bias for {\gten} but a $w$ biased high for {\celeven}. This decrease in error is not statistically significant as we have statistical uncertainty of $\sim0.01$ for $100$ simulation realisations. The average bias over the two scatter models is $+0.028$, representing a larger bias than the BBC method.

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{tikz}
\usepackage{enumerate}
%\usepackage{tabu}
%\usepackage{tabularx}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\usetikzlibrary{bayesnet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}
	\centering
	\caption{ Parameters defined in our model and a summary of their use. The parameters are broken into multiple sections, the top for parameters which are defined globally across all surveys, the second section for parameters which are defined for each survey, the third section are parameters which are defined for each supernova. The bottom section shows the observables (not parameters) that are the input data to the model.}
	\label{tab:param_summary}
	\begin{tabular}{ll}
		\hline
		Parameter & Description \\
		\hline
		$\Omega_m$  & Matter density  \\
		$w$  &  Dark energy equation of state  \\
		$\alpha$ & Stretch standardisation   \\
		$\beta$         &  Colour standardisation   \\
		$\delta(0)$ & Scale of the mass-magnitude correction\\
		$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
		$\delta\mathcal{Z}_i$ & Systematics scale\\
		$\langle M_B \rangle$ & Mean absolute magnitude \\
		%$s_c$ & Colour bias\\
		\hline
		$\delta S$ & Selection effect deviation \\
		$\langle x_1^i \rangle$ & Mean stretch nodes\\
		$\langle c^i \rangle$ & Mean colour nodes\\
		$\alpha_c$ & Skewness of colour population \\
		$\sigma_{M_B}$ & Population magnitude scatter \\
		$\sigma_{x_1}$ & Population stretch scatter \\
		$\sigma_{c}$ & Population colour scatter \\
		$\kappa_{0}$ & Extra colour dispersion\\
		$\kappa_{1}$ & Redshift-dependence of extra colour dispersion\\
		\hline
		$m_B$ & True flux\\
		$x_1$ & True stretch \\
		$c$ & True colour \\
		$z$ & True redshift \\
		$M_B$ & Derived absolute magnitude \\
		$\mu$ & Derived distance modulus \\
		\hline
		$\hat{m}_B$ & Measured flux\\
		$\hat{x}_1$ & Measured stretch \\
		$\hat{c}$ & Measured colour \\
		$C$ & Covariance on flux, stretch and colour \\
		$\hat{z}$ & Observed redshift \\
		$\hat{m}$ & Determined mass probability \\
		$\hat{p}$ & Determined {\green Ia} probability \\
		\hline
	\end{tabular}
\end{table}

@@

	\node[det, above=of z] (mu) {$\mu$};
	\node[latent, right=4.33cm of mu] (MBobs) {$M_B$};
	% Survey nodes
	\node[latent, above=of sum, yshift=1cm,text width=2.7cm, align=center] (pop1) {$\langle x_1^i \rangle, \langle c^i \rangle,\sigma_{M_B}, $\\$ \sigma_{x_1}, \sigma_c, \alpha_c, \kappa_0, \kappa_1$ };
	\node[latent, right=1.5cm of pop1, align=center] (sf) {$\delta S$};
	% Global nodes
	\node[latent, above=2cm of mu]  (cosmo) {$\Omega_m, w$};
	\node[latent, above=1.7cm of MBobs, text width=3cm, align=center]  (ab) {$\langle M_B \rangle, \alpha, \beta$, $\delta(0)$, \\$\delta(\infty)$, $\delta \mathcal{Z}_i$};

@@

In addition to the improvements in the scatter models over the simple data, we also include peculiar velocities for the LowZ sample, and our full treatment of systematics. Our simulated populations are sourced from \citet[][hereafter {\sk}]{Scolnic2016} and shown in Table \ref{tab:dist}. Initial tests were also done with a second, Gaussian population with colour and stretch populations centered on zero and with respective width $0.1$ and $1$, however cosmological parameters were not impacted by choice of the underlying population and we continue using only the {\sk} population for computational efficiency. The selection effects were quantified by comparing all the generated supernovae to those that pass our simulated cuts, as shown in Figure~\ref{fig:sf_snana}. It is from this simulation that our analytic determination of the selection functions for the LowZ and DES survey are based. {\green We run two simulations to determine the efficiency using the {\gten} and {\celeven} scatter models and find no difference in the Malmquist bias between the two models.}

@@

\begin{table*}
	\centering
	\caption{Standardisation parameters and base intrinsic scatter parameter results for the 100 fits to {\gten} and {\celeven} simulations. We show the average parameter mean and standard deviation, with the simulation scatter shown in brackets. Truth values for the simulations are $\alpha=0.15$, $\langle M_B \rangle = -19.365$, $\beta_{\rm G10} = 3.1$, $\beta_{\rm C11} = 3.8$.  The width of the intrinsic scatter does not have an input truth value as it is determined from the scatter model, with {\gten} having 70\% achromatic scatter and {\celeven} only having 25\% achromatic scatter.}
	\label{tab:standardisation}
	\begin{tabular}{l|ccccc}
		\hline
		Model & $\alpha$ & $\beta$ & $\langle M_B \rangle$ & $\sigma_{m_B}^0$ &  $\sigma_{m_B}^1$ \\
		\hline
		{\gten} Stat + Syst  & $0.152\pm0.009\ (0.008)$ & $ 3.44\pm0.19\ (0.18)$ & $-19.367\pm0.028\ (0.015)$ & $0.070\pm0.022\ (0.018)$ & $0.073\pm0.025\ (0.022)$\\
		{\gten}  Stat         & $0.150\pm0.008\ (0.008)$ & $3.43\pm0.20\ (0.17)$ & $-19.374\pm0.016\ (0.013)$ & $0.069\pm0.023\ (0.019)$ & $0.072\pm0.026\ (0.023)$\\
		{\celeven} Stat + Syst  &  $0.152\pm0.009\ (0.007)$ & $3.76\pm0.15\ (0.13)$ & $-19.351\pm0.030\ (0.018)$ & $0.024\pm0.016\ (0.011)$ & $0.029\pm0.020\ (0.014)$ \\
		{\celeven} Stat         &  $0.150\pm0.008\ (0.007)$ & $3.75\pm0.16\ (0.13)$ & $-19.359\pm0.016\ (0.015)$ & $0.025\pm0.016\ (0.012)$ & $0.027\pm0.020\ (0.015)$\\
		\hline
	\end{tabular}
\end{table*}

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_points_g10.pdf}		\includegraphics[width=\columnwidth]{bulk_points_c11.pdf}
	\end{center}
	\caption{Maximum posterior points for 100 realisations of supernova data for two intrinsic dispersion models - the {\gten} model for the top panel and the {\celeven} model for the bottom panel. Points are shown for parameters $\Omega_m$, $w$, $\alpha$ and $\beta$, with the other fit parameters being marginalised over. As we are unable to fully correct observed summary statistics, a step required by the lack of intrinsic scatter in the SALT2 model, we expect to see an offset in $\alpha$ and $\beta$. This in turn effects cosmology, resulting in small biases in $w$.}
	\label{fig:bulk_posterior}
\end{figure}

\begin{table}
	\centering
	\caption{Investigating the combined 100 fits to {\gten} and {\celeven} simulations, fitting with both statistics only and also when including systematics. The quoted value for $w$ represents the average mean of the fits, with the uncertainty being the average standard deviation of the fits. In brackets, the simulation scatter (the standard deviation of the mean of 100 fits) is shown, and the bias significance represents our confidence that the deviation in the mean $w$ away from $-1$ is not due to statistical fluctuation. With systematics enabled, both the {\gten} and {\celeven} models show evidence of bias, scattering to either side of the simulated value of $w=-1$. However, their deviation from the truth value represents a shift of approximately $0.5\sigma$ when taking into account the uncertainty on fits to $w$. The bias is sub-dominant to both the size of the uncertainty for each fit, and the scatter induced by statistical variance in the simulations. We also note that the simulations do not vary cosmological parameters nor population. As our model does include uncertainty on those values, the simulation scatter is expected to be less than the model uncertainty, and represents a minimum bound on permissible uncertainty values.}
	\label{tab:bulk_summary}
	\begin{tabular}{l|cc}
		\hline
		Model & $w$ (scatter) & $w$-Bias \\
		\hline
		{\gten} Stat + Syst  &  $-0.998\pm 0.097\ (0.073)$ & $(0.02\pm0.07)\sigma$  \\
		{\gten}  Stat         &  $-1.008\pm 0.080\ (0.068)$ & $(-0.10\pm0.08)\sigma$   \\
		{\celeven} Stat + Syst  &  $-0.945\pm 0.098\ (0.077)$ & $(0.55\pm0.08)\sigma$  \\
		{\celeven} Stat         &  $-0.948\pm 0.079\ (0.066)$ & $(0.65\pm0.08)\sigma$   \\
		\hline
	\end{tabular}
\end{table}

@@

Points of maximum posterior for 100 data realisations are shown in Figure \ref{fig:bulk_posterior}. The parameter bounds and biases for $w$ are listed in Table \ref{tab:bulk_summary},  {\green and secondary parameters are shown in Table \ref{tab:standardisation}. Our recovered results for $w$ are all within $0.5\sigma$ of the true values of $w=-1$. Table \ref{tab:standardisation} shows a clear difference in both $\beta$ and $\sigma_{m_B}$ across the {\gten} and {\celeven} simulations. As expected, the {\celeven} simulations recover a far smaller intrinsic magnitude scatter, giving results of approximately $0.025$ when compared to the result of $0.070$ for the {\gten} simulations. The extra smearing of the {\celeven} model does not result in a biased $\beta$ value, with recovery of $\beta\approx3.76$ close to the input truth value of $3.8$, however the $\beta$ recovery for the {\gten} simulations is biased high, finding $\beta\approx3.44$ with an input of $3.1$. Interestingly, $w$-bias is only found for the {\celeven} simulations.}

@@

Unfortunately, adding extra fit parameters to allow for shifting observables {\green washes out our ability to constrain cosmology, and applying a specific bias correction requires running a fiducial simulation (assuming cosmology, population and scatter model), which presents difficulties when trying to account for correlations with population and scatter model.} This is compounded by the fact that bias corrections do not in general improve fits (increase the log posterior), and so are difficult to fit parametrically. Works such as \citet{Kessler2017} show that bias corrections can be applied to supernovae datasets that can robustly handle multiple intrinsic scatter models, and future work will center on uniting these methodologies - incorporating better bias corrections that separate intrinsic scatter bias and non-Gaussian summary statistic bias from Malmquist bias, without having to precompute standardisation parameters and populations.

@@

Table \ref{tab:parameter_correlations} lists the fit correlations between our model fit parameters (excluding the LowZ band systematics, and Malmquist bias uncertainty parameters which had negligible correlation), showing (in order) cosmological parameters, standardisation parameters, population width and skewness parameters, intrinsic dispersion parameters, mass-step parameters, population mean parameters, SALT2 model systematics, dust systematic, global HST calibration systematic, peculiar velocity systematic, global redshift systematic and DES band magnitude and wavelength systematics. Figure \ref{fig:bulk_cor} show the full correlations between all non-systematic model parameters. {\green As expected, $w$ bias would be introduced primarily through incorrectly determined standardisation parameters, mean absolute magnitude or incorrect dispersion parameters. As discussed previously, the culprit for our $w$-bias is the dispersion model, rather than standardisation parameters}. Other interesting correlations are shown and discussed in Figure \ref{fig:bulk_cor}. The band systematics for DES filters $g$, $r$ and $i$ also show significant correlation with $w$, highlighting the importance of minimising instrumental uncertainty.

@@

\begin{table*}
	\centering
	\caption{The error budget on $w$, as determined from analysing uncertainty on simulation data whilst progressively enabling model features. We start from the top of the table, only varying cosmological parameters $\Omega_m$ and $w$, and then progressively unlock parameters and let them fit as we progress down the table. The cumulative uncertainty shows the total uncertainty on $w$ on the fit for all, where the $\sigma_w$ term is derived by taking the quadrature difference in cumulative uncertainty as we progress.}
	\label{tab:uncert}
	\begin{tabular}{l|l|rr}
		Feature & {\green Parameters} & $\sigma_w$ & Cumulative  \\
		\hline
		Cosmology                      & $\Omega_m$, $w$ & 0.051  &   0.051       \\
		Standardisation                & $\alpha$, $\beta$, $\langle M_B \rangle$, $\delta(0)$, $\delta(\infty)/\delta(0)$ & 0.046  &   0.068       \\
		Intrinsic scatter              & $\kappa_0$, $\kappa_1$ & 0.020  &   0.071       \\
		Redshift-independent populations             & $\sigma_{M_B}$, $\sigma_c$, $\sigma_{x_1}$, $\alpha_c$ & 0.022  &   0.074       \\
		Redshift-dependent populations & $\langle c_i \rangle$, $\langle x_{1,i} \rangle$ & 0.030  &   0.080   \\
		Systematics                    & $\delta \mathcal{Z}_i$, $\delta S$ & 0.054  &   0.096      \\ 
		\hline
	\end{tabular}
\end{table*}

@@

@@

{\green As shown in \citet{Brout18SYS}, BBC recovers cosmological parameters without bias so long as the intrinsic scatter model is known. As we do not know the correct intrinsic scatter model, the BBC method averages the results when using bias corrections from {\gten} and from {\celeven}. As such, we expect the BBC method to be biased in one direction for {\gten} simulations and the other direction for {\celeven} simulations. These results are consistent with those displayed in Table \ref{tab:bulk_summary_bbc}, as both} BBC and BHM are sensitive to the intrinsic scatter model, finding differences of $\sim0.06$ in $w$ when varying the scatter model. The BBC method finds $w$ biased low for G10 and $w$ biased high for C11 (by about $\pm0.03$), so taking the average result only results in a small bias of $-0.01$ in $w$. Our method shows a small improvement in the insensitivity to the intrinsic scatter model, finding no bias for {\gten} but a $w$ biased high for {\celeven}. This decrease in error is not statistically significant as we have statistical uncertainty of $\sim0.01$ for $100$ simulation realisations. The average bias over the two scatter models is $+0.028$, representing a larger bias than the BBC method.
